Caring and Feeding the Wild Caught Data

### 2021-03-03 report_alt.Rmd
author order changed. Di last. Middle authors alphabetical

---
title: "Caring and Feeding the Wild Caught Data"
subtitle: "A Case of The NLSY79 Data"
author: "Dewi Amaliah, Dianne Cook, Emi Tanaka, Nicholas Tierney, Kate Hyde"
date: "24/02/2021"
output: 
  bookdown::pdf_document2:
    toc : false
bibliography: references.bib
---

>>>>

---
title: "Caring and Feeding the Wild Caught Data"
subtitle: "A Case of The NLSY79 Data"
author: 
 - Dewi Amaliah
 - Kate Hyde
 - Emi Tanaka
 - Nicholas Tierney
 - Dianne Cook
date: "24/02/2021"
output: 
  bookdown::pdf_document2:
    toc : false
bibliography: references.bib
---
